\documentclass{article}
\title{BIL 101 \\ INTRODUCTION TO COMPUTER SCIENCE \\ HW09}
\date{}
\begin{document}
\maketitle
\section{Answer}
In order to talk about Reinforcement :   As we know the Reinforcement learning is one of the filed or lets say an area of machine learning  and a part of the operant conditioning in computer deep leaning field there is two kinds of operant conditioning , one is punishment which is in other world(Decrease behavior) and the second one is Reinforcement which we called it as (increase behavior) . and the Reinforcement  is the part of deep learning which will helps us to understand a lot about gamming and how to gamming. And it has plenty of parts in it like some of them field called Statistic ,genetic algorithms information theory or more . and this topic( the Reinforcement learning )is thought in a field of computer science   called “approximate dynamic programming”. And Reinforcement has divided to two parts which are : (Positive) and the other is we called (negative).and if we are going to talk about the difference between reinforcement and other kinds of deep learning for example let us take difference between punishment which is also a field fo deep learning and reinforcement : \\
\\\textbf{ a)}
\\the first difference between reinforcement and punishment is ,a reinforcer strengthens a behavior in the other hand a punisher weakens a response.
\\\textbf{b)}
\\the second difference is ,a reinforcer increases its probability and a punisher decreases 
its probability.
\section{Answer}
for the definition of three kinds of operations which are(image processing ,three dimensional and two dimensional objects) we can say that :
\\\textbf{1}) IMAGE PROCESSING TECHNIQUES:
\\Image processing is a method to perform  some operations on an image, in order to get an enhanced image or to extract some useful information from it. It is a type of signal processing in which input is an image and output may be image or characteristics joined with that image.i will mention the name of some techniques of image processing which will also indicates the differences of it which other kinds of processing:
\\\textbf{a})Image editing
\\\textbf{b}) Independent component analysis.
\\\textbf{c}) Linear filtering.
\\\textbf{d}) Partial differential equations.
\\
\\\textbf{2}) TWO DIMENSIONAL GRAPHIC TECHNIQUES:
\\in 2D or two dimensiona graphic techniques we focus on converting or changing the two dimensional materials or let us say shapes like cyclic polygon,tangential polygon or so on  it converts these kinds of shapes to the pixels which the cells of a picture.
\\\textbf{3}) THREE DIMENSIONAL GRAPHIC TECHNIQUES:
\\ three dimensional or 3D techniques are also differs fro other kinds of images techniques .by three dimensioal techniques we can convert the 3D shapes like spheres,cubes or so on ,to the images. 
\\ and finally let us talk abit about the process of the three dimensional graphics:
\\ there is three steps to execute this process:
\\ 3D computer graphics consists of  three basic steps which are:
\\ 1) 3D modeling –  which is the process of forming a computer model of an object's shape
\\2) animation – the placement and movement of objects within a scene callaed animation .
\\3)3D rendering – the computer calculations that, based on light placement, surface types, and other qualities, generate the image.
\end{document}
